\documentclass[twocolumn,english,compsoc,journal]{IEEEtran}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage[unicode=true,
 bookmarks=true,bookmarksnumbered=true,bookmarksopen=true,bookmarksopenlevel=1,
 breaklinks=false,pdfborder={0 0 0},backref=false,colorlinks=false]
 {hyperref}
\hypersetup{pdftitle={Your Title},
 pdfauthor={Your Name},
 pdfpagelayout=OneColumn, pdfnewwindow=true, pdfstartview=XYZ, plainpages=false}
\usepackage{breakurl}

\makeatletter

%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

 % protect \markboth against an old bug reintroduced in babel >= 3.8g
 \let\oldforeign@language\foreign@language
 \DeclareRobustCommand{\foreign@language}[1]{%
   \lowercase{\oldforeign@language{#1}}}

% for subfigures/subtables
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\usepackage[nocompress]{cite} %optional

\makeatother

\begin{document}



\title{DroidStealth: A Nomadic Data Obfuscation Tool that Facilitates Sharing}


\author{Olivier Hokke, Alex Kolpa, Joris van den Oever, and~Alex Walterbos}


\markboth{Delft University of Technology Student Project}{Your Name \MakeLowercase{\textit{et al.}}: Your Title}

\IEEEtitleabstractindextext{
\begin{abstract}
TODO ABSTRACT TEXT\end{abstract}

\begin{IEEEkeywords}
casual search, privacy, nomadic software, obfuscation
\end{IEEEkeywords}

}

\maketitle

\IEEEdisplaynontitleabstractindextext{}


\IEEEpeerreviewmaketitle{}


\section{Introduction}

\IEEEPARstart{W}{ith} the rising use of smart phones in daily life and
exceptional events means sensitive data is commonly available on phones.
These pictures, videos, and in some cases other files are very interesting
to a wide variety of groups. And sometimes the standard protections on
the phone are not enough to keep those groups out. Just slide the screen
and full access to everything. Even if there things like a password or
unlock patterns these can be forced out of a person. Followed by a simple
search through the phones files by hand to find what they desire.

We call such non-technical searches of devices 'casual search.' The
person performing it will have varying degrees of expertise regarding
the workings of smartphones but is limited to the tools already available
on the phone to check out data. Instead of performing advanced attacks
using specialized tools designed to get all the data out of a phone.

This project aims to address only the issues with casual search through
the use of an Android app. The tool aided expert attacks are not within the
scope of this project. As this is a very different kind of problem.

\textbf{Bla bla bla structure of paper and what we're going to discuss
where.}


\input{problemdescription}

\include{approach_design}

\section{Implementation}

How did we create the data vault. Encryption, thumbnails, notifications
for unlocking.

What we do to make morphing possible.

\input{morphing}

\include{encryption-implementation}

\section{Future Work}

There are several aspects of the application than can be improved. Which
can be categorized under one of the following: usability, and morphing.
The categories will be discusses individually as they are separated both
technically and conceptually. 

\subsection{Usability}

In terms of usability there has been no formal study on what aspects of
the application work work well. However informal testing has shown several
avenues of improvement. First is how to access the application. 

While the freely chosen app name and icon do suffice there are other ways 
it could be done. Namely the widgets available to android users. This could 
be a simple widget mimicking the standard available widgets, or even be 
invisible. So as to have no recognizable screen space. While it could still
react to certain use patterns. A first implementation of this functionality is
available but needs to be properly evaluated.

Once the application has been started there are still some ways the user
needs to be observant in how she uses the application. As it can result in
inadvertent data breaches. Mainly when the data is opened in other apps.
While several solutions have been discussed, like listening to home button
presses or having files only be unlocked for limited time, these still need
to be explored in depth.

\subsection{Morphing} 

When it comes to morphing there are two major limitations; app renaming and software integrity validation. 
The first pertains to limitations in the renaming of the application when morphing. 
The second holds that there is no way to guarantee that the application hasn't been modified after morphing.

When it comes to naming there is a functional limitation in the length of the new name as of now.
It has to be the same length or shorter than the original name length, which can be padded with whitespace. 
But as of yet the way Android manifests are encoded are opaque enough that not all size indicators have been correctly identified.

The other component of naming is the `package name' staying consistent across morphs. 
The package name of an application is a naming convention which Android uses as an identifier for applications in its app store.
For casual searches, the package name is not relevant in most situations.
However there is one exception, namely if DroidStealth would be on an app store. 
As apps are identified there by package name this would make it easy to reveal its presence just by searching for it on the appstore.
Currently the only solution is to not be available through any app store.

The integrity validation is currently something that does not exist with morphing. 
The application needs to be signed with the same key before morphing as after morphing if users want to be able to reinstall it afterwards without first having to remove it. 
This makes it possible to distribute updates in a nomadic manner, but also means the signing key has to be packaged with DroidStealth for it to work. 
As such anyone can create a modified version of the application and spread that as an `update.'
Solving this problem is non-trivial and requires more research.

\subsection{Security}
A potential security threat that can be exploited, is that
unlocked files are stored on the internal SD card of the device,
and that another app could constantly watch the folders in which
those files would be decrypted. Then this other app could save
them somewhere else or send them over the Internet.

Also, if files are unlocked, and the user's device is taken from
its rightful owner without warning, then the user might not have
gotten enough time to press the notifications to swiftly lock
the secret files back. Invaders won't be able to see the data
directly, unless they launch a file browser and start searching,
but they would be informed of the existence of secret files.
This could be a potential danger, because an attacker could be
interested in those files and do the user harm to get these
files. Users should be fully aware that they should only unlock
files if they are 100\% sure that they are in a safe location.

\section*{Acknowlegments}

The authors would like to thank Dhr JA Pouwelse from the Delft University of Technology for providing the possibility to investigate this matter, for providing his helpful insights and feedback, and placing his expertise at our disposal.

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
